%-------------------------
% Katy Felkner's CV
% adapted from template by Sourabh Bajaj
% https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\setlength{\footskip}{4.08003pt}

% formatting for links
\usepackage[pdftex]{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% manage publication list
\usepackage[style=authoryear, sorting=ydnt, minnames=2, dashed=false ]{biblatex}
\AtBeginBibliography{\small}

\renewcommand*{\mkbibcompletename}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}  
}

% text encoding stuff to make this ATS-parseable
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItemWithHeader}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
  {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSecondTitle}[2]{
  \vspace{-3pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

% tentatively keeping this in a tabular to make it more identical to other headings
\newcommand{\resumeSubheadingNoTitle}[1]{
  \vspace{-1pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\textbf{\LARGE Katy Felkner}

\href{mailto:felkner@isi.edu}{\texttt{felkner@isi.edu}}~\textbar~ \href{http://katyfelkner.com/}{\texttt{http://www.katyfelkner.com}}~\textbar~(405)-808-2703


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA}
      {Ph.D. in Computer Science}{Aug. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Expected Spring 2027; GPA: 3.88/4.00; Supported by \textbf{NSF Graduate Research Fellowship}}
      \resumeItem{Coursework: Advanced Natural Language Processing, Fairness in AI, Probability and Statistics for Data Science, Representation Learning in NLP, Advanced Algorithms, Crafting a Research Agenda in Computer Science}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Oklahoma}{Norman, OK}
      {B.S. in Computer Science \textit{(summa cum laude)}, B.A. in Letters \textit{(summa cum laude)}}{Aug. 2016 -- May 2020}
      \resumeItemListStart
        \resumeItem{Minor: Mathematics; GPA: 4.00/4.00} 
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Research Interests}
\small{My research focuses on developing high-quality, \textbf{well-grounded benchmark datasets} for robust evaluation of language models, with particular emphases on participatory, community-engaged methods and on rigorous measurement of fairness and social bias.}

\section{Publications}
\begin{refsection}[my_pubs_formatted.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

\section{Technical Skills}
 \resumeSubHeadingListStart
   \resumeItemWithHeader{Programming Languages and Skills}{Python, C, C++, R, SQL, Bash Scripting, HPC, Slurm}
   \resumeItemWithHeader{ML/NLP/Data Science Tools}{HuggingFace, PyTorch, TensorFlow, SpaCy, Pandas, Numpy, Scikit-Learn, NLTK}
 \resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {LLM Fairness and Bias, USC Information Sciences Institute}{Los Angeles, CA}
      {Graduate Research Assistant}{Jan. 2022 -- Present}
      \resumeItemListStart
      \resumeItem{Developed two community-sourced benchmark datasets for detecting anti-LGBTQ+ and antisemitic bias in LLMs.}
      \resumeItem{Designed and distributed two community surveys and analyzed 500 responses to inform LLM bias benchmarks.}
      \resumeItem{Led team of 3 to collect 8M sentences of community data, then train 32 debiased models via continued pretraining.}
      \resumeItem{Assessed LLM capability to assist in data annotation for fairness benchmark construction and conducted detailed human analysis of model failures.}
      \resumeItem{Analyzed behavior of textual entailment (natural language inference, NLI) as an LLM bias metric, including developing a novel NLI bias dataset and detailed study of differences in behavior between token probability and NLI bias metrics.}
      \resumeItemWithHeader{Publications}{Led interdisciplinary teams of coauthors to write and publish two papers in ACL (2023, 2024).}
      \resumeItemWithHeader{Mentoring}{Currently mentoring undergraduate student on NLI bias metric project.}
      \resumeItemWithHeader{Advisor/PI}{Jonathan May}
      \resumeItemListEnd

    \resumeSubheading
      {DARPA ReMATH, USC Information Sciences Institute}{Los Angeles, CA}
      {Graduate Research Assistant}{Jan. 2021 -- Jun. 2022}
      \resumeItemListStart
      \resumeItem{Trained neural machine translation (NMT) models for extraction of symbolic math from assembly code and bit-vector expressions.}
      \resumeItem{Developed novel metrics for evaluation of NMT-generated mathematical expressions.}
      \resumeItemWithHeader{Publication}{Wrote relevant sections of workshop paper accepted to CheckMATE, ACM CCS 2021.}
      \resumeItemWithHeader{PI}{Luis Garcia}
      \resumeItemListEnd

    \resumeSubheading
      {Border Translation Project, USC Information Sciences Institute}{Los Angeles, CA}
      {Graduate Research Assistant}{Aug. 2020 -- Dec. 2021}
      \resumeItemListStart
      \resumeItem{Built and evaluated NMT systems for extremely low-resource languages.}
      \resumeItem{Developed baseline NMT system for K'iche', a Mayan indigenous language, with intended application of helping NGOs provide legal assistance to immigrants and asylum seekers.}
      \resumeItemWithHeader{Advisor/PI}{Jonathan May}
      \resumeItemListEnd

    \resumeSubheading
      {Ultrascale Systems Research Center, Los Alamos National Laboratory}{Remote}
      {Post-Baccalaureate Research Intern}{May 2020 -- Aug. 2020}
      \resumeItemListStart
      \resumeItem{Collected 750,000 lines of non-secret syslog data using a 20-node virtual compute cluster.}
      \resumeItem{Tested several word embedding and clustering algorithms to extract natural language features from supercomputer syslog.}
      \resumeItem{Showed that these natural language features can be used to improve HPC node failure detection and prediction.}
      \resumeItemWithHeader{Publication}{Wrote workshop paper accepted to Second Workshop on Machine Learning for Computing Systems, Supercomputing 2020.}
      \resumeItemWithHeader{Mentor}{Elisabeth (Lissa) Moore}
      \resumeItemListEnd

    \resumeSubheading
      {Digital Latin Library, University of Oklahoma}{Norman, OK}
      {Undergraduate Research Assistant}{Jan. 2017 -- May 2020}
      \resumeItemListStart
      \resumeItem{Wrote Python scripts to parse HTML documents containing Latin texts, generating 125000 lines of SQL output.}
      \resumeItem{Designed scripts to automate XML encoding of Latin prose and poetry, reducing time to encode by a factor of 400.}
      \resumeItem{Only undergraduate student accepted to National Endowment for the Humanities Institute on Advanced Topics in Digital Humanities for Summer 2018 at Tufts University.}
      \resumeItemWithHeader{Presentations}{Conference talks at Society for Classical Studies 2019, Classical Association of the Middle West and South 2018, National Conference on Undergraduate Research 2018}
      \resumeItemWithHeader{Mentor}{Samuel Huskey}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Teaching Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {CSCI 662 Advanced Natural Language Processing, University of Southern California}{Los Angeles, CA}
      {Teaching Assistant}{Fall 2025}
      \resumeItemListStart
      \resumeItem{Substantially update all homework assignments to better cover finetuning, attention, transformers, and RLHF.}
      \resumeItem{Migrate automated grading for all programming assignments from Vocareum to Gradescope.}
      \resumeItem{Configure all GradeScope assignments and rubrics.}
      \resumeItem{Grade assignments, including programming homework, written reports, and in-class presentations.}
      \resumeItem{Manage course logistics for about 30 students, including webpage, Slack channel, and Brightspace LMS.}
      \resumeItem{Host weekly office hours and answer student questions on Slack.}
      \resumeItemWithHeader{Professor}{Jonathan May}
      \resumeItemListEnd

      \resumeSubheading
      {CSCI 350 Introduction to Operating Systems, University of Southern California}{Los Angeles, CA}
      {Teaching Assistant}{Summer 2025}
      \resumeItemListStart
      \resumeItem{Graded C programming assignments in XV6 teaching operating system.}
      \resumeItem{Hosted weekly office hours and answer student questions on Piazza.}
      \resumeItemWithHeader{Professor}{Bill Cheng}
      \resumeItemListEnd
    \resumeSubHeadingListEnd



\section{Work Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Epic Systems Corporation}{Madison, WI}
      {Software Developer Intern}{May 2019 -- Aug. 2019}
      \resumeItemListStart
      \resumeItem{Prototyped a menstrual cycle tracking feature within MyChart for iOS to allow patients to share cycle data with providers.}
      \resumeItem{Designed and implemented server and client-side data structures to save cycle data to the patient's medical record.}
      \resumeItem{Built four complete and interactive user-interface screens and partial prototypes of several others.}
      \resumeItem{Conducted user research, including about 100 internal survey responses and 5 user interviews.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Presentations}
\resumeSubHeadingListStart
 \resumeSubheadingNoTitle{Invited Talks}
      \resumeItemListStart
      \resumeItem{Celebrate Track Invited Speaker, \textit{Community-Sourced Bias Metrics for LLMs}, UCLA QWERHacks. \hfill \textit{Feb. 2025}}
      \resumeItem{Guest Lecturer on \textit{Ethics and Power in NLP}, USC CSCI 662 Advanced NLP \hfill \textit{Fall 2023, 2024, 2025}}
      \resumeItem{Invited Panelist on \textit{Language Matters: Addressing Bias in LLMs}, IAPP Privacy. Security. Risk. \hfill \textit{Sep. 2024}}
      \resumeItem{Invited Speaker, John Brooks Slaughter Leadership in Engineering DEI Summit. \hfill \textit{Feb. 2024}}
      \resumeItem{Invited Panelist on \textit{Bias in Generative AI}, QueerInAI Workshop at NeurIPS. \hfill \textit{Dec. 2023}}
    \resumeItem{Invited Speaker, \textit{Anti-Queer Bias in LLMs}, USC ISI Natural Language Seminar. \hfill \textit{Jun. 2022}}
    \resumeItem{Guest Lecturer, \textit{Servius: An Object-Oriented Approach}, Sunoikisis Digital Classics \hfill \textit{May 2019}}
      \resumeItemListEnd
    \resumeSubheadingNoTitle{Conference Talks and Posters}
      \resumeItemListStart
      \resumeItem{Lightning Talk, \textit{Participatory Methods for LLM Bias Benchmarks}, Responsible Data Workshop. \hfill \textit{Sep. 2025}}
      \resumeItem{Poster Presentation, \textit{Textual Entailment as a Bias Evaluation Metric for LLMs}, USC ShowCAIS. \hfill \textit{Apr. 2025}}
      \resumeItem{Poster Presentation, \textit{GPT is Not an Annotator}, Southern California NLP Symposium. \hfill \textit{Nov. 2024}}
      \resumeItem{Roundtable Discussion, \textit{Defining and Disrupting Antisemitism}, Association for Jewish Studies. \hfill \textit{Dec. 2023}}
      \resumeItem{Poster Presentation, \textit{Anti-Queer Bias in LLMs}, CRA-WP Grad Cohort for Women. \hfill \textit{Apr. 2023}}
      \resumeItem{Poster Presentation, \textit{Anti-Queer Bias in LLMs}, Southern California NLP Symposium. \hfill \textit{Nov. 2022}}
      \resumeItem{\textit{Automatically Encoding Digital Editions of Latin Texts}, Society for Classical Studies. \hfill \textit{Jan. 2019}}
      \resumeItem{\textit{Coding And/As Classical Scholarship}, Classical Association of the Midwest and South. \hfill \textit{Apr. 2018}}
      \resumeItem{\textit{Coding And/As Classical Scholarship}, National Conference on Undergraduate Research. \hfill \textit{Apr. 2018}}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

% TODO Professional Service
\section{Professional Service}
  \resumeSubHeadingListStart
    \resumeSubheading
      {USC ISI Natural Language Seminar}{Los Angeles, CA}
      {Coordinator}{Aug. 2024 -- May 2025}
      \resumeItemListStart
        \resumeItem{Recruited external speakers and coordinated publicity for 15 talks, average 20 attendees each.}
        \resumeItemListEnd
    \resumeSubheadingNoTitle{Conference and Workshop Reviewing}
      \resumeItemListStart
        \resumeItemWithHeader{Conferences}{EMNLP 2023, ACL 2023, EMNLP 2022 Theme Track}
        \resumeItemWithHeader{Workshops}{NAACL Student Research Workshop 2025}
        \resumeItemWithHeader{Ethics Reviewing}{EMNLP 2025}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Leadership and Outreach}
\resumeSubHeadingListStart
    \resumeSubheading
    {USC Center for AI in Society} {Los Angeles, CA} {Student Leader} {Aug. 2025 -- Present}
    \resumeItemListStart
    \resumeItem{Assist with publicizing seminars, mentoring CAIS++ undergraduates, and organizing ShowCAIS Symposium.}
    \resumeItemListEnd
    \resumeSubheading {Queers in Engineering, Science, and Technology (QuEST)} {Los Angeles, CA} {Graduate Representative} {Sep. 2020 -- Present}
    \resumeItemListStart
    \resumeItem{Recruit graduate students to QuEST and advocate for their needs in the organization.}
    \resumeItem{Organize general meetings on graduate school/fellowship applications and mentor undergraduate applicants.}
    \resumeItem{2022 oSTEM Region F Conference Organizer: Presented graduate application workshop, spoke on Queer in Academia panel, organized and hosted charity livestream, raising \$950 for LGBTQ+ community organizations in LA}
    \resumeItemListEnd
    
    \resumeSubheading {Alpha Sigma Kappa -- - Women in Technical Studies} {Norman, OK} {President}{Apr. 2019 -- Apr. 2020}
    \resumeItemListStart
    \resumeItem{Oversaw 6 executive board members and served as chief risk management officer.}
    \resumeItem{Led chapter’s transition to virtual operations due to COVID-19, rapidly establishing new programs to maintain sisterhood and encourage academic excellence during the pandemic.}
    \resumeItemListEnd
    \resumeSubheadingSecondTitle{Vice President}{Dec. 2017 -- Dec. 2018}
    \resumeItemListStart
    \resumeItem{Planned and executed nine recruitment events per semester, recruiting 32 new members.}
    \resumeItem{Mentored 9 officers on 5 committees, resulting in successful chapter social and new member education programs.}
    \resumeItemListEnd
    \resumeSubheading
    {Out in Science, Technology, Engineering, and Math} {Norman, OK}
    {Secretary} {Mar. 2017 -- Dec. 2019}
    \resumeItemListStart
    \resumeItem{Served on founding executive board of first oSTEM chapter in the state of Oklahoma.}
    \resumeItem{Planned and executed about two medium-scale events per month and managed event promotion and member communication.}
    \resumeItemListEnd
    \resumeSubheading
    {Halliburton Women's Welcome} {Norman, OK}
    {Program Committee Chair} {Aug. 2018, Aug. 2019}
    \resumeItemListStart
    \resumeItem{Served on founding executive board of first oSTEM chapter in the state of Oklahoma.}
    \resumeItem{Planned and executed a week-long program for 80+ incoming female students in engineering.}
    \resumeItem{Organized campus resource fair and inclusive professional dress workshop that received 91\% positive participant feedback.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Honors and Awards}
 \resumeSubHeadingListStart
 \resumeSubheadingNoTitle{University of Southern California}
 \resumeItemListStart
   \resumeItem{National Science Foundation Graduate Research Fellowship: 3 year selective national fellowship}
   \resumeItem{Viterbi Graduate School Fellowship: 1 year USC internal fellowship}
\resumeItemListEnd
\resumeSubheadingNoTitle{University of Oklahoma}
\resumeItemListStart
   \resumeItem{Gallogly College of Engineering Outstanding Senior}
   \resumeItem{Outstanding Senior in Computer Science}
   \resumeItem{Letzeiser Honor List – Silver Medalist: second place among top 30 seniors at University of Oklahoma}
   \resumeItem{Outstanding Greek Senior: awarded to about 5 seniors per year for fraternity/sorority leadership}
   \resumeItem{Ronald Lehr Phi Beta Kappa Undergraduate Research Award: best presentation at OU Undergrad Research Day}
   \resumeItem{Alpha Sigma Kappa National Outstanding Leader}
   \resumeItem{OU Campus Life Award: 40 outstanding upperclassmen based on campus leadership}
   \resumeItem{Regents' Award for Outstanding Juniors: 12 most outstanding juniors, based on academics and campus leadership}
   \resumeItem{President’s Award for Outstanding Sophomores: 12 most sophomores, based on academics and campus involvement}
   \resumeItem{Rita H. Lottinville Prize: five outstanding sophomores, based on academic and extracurricular achievement}
   \resumeItem{University College PACE Award: up to 1\% of freshman class based on leadership and community involvement}
   \resumeItem{Myrna L. Carney Award – given to three students from among PACE award winners}
   \resumeItem{Douglas and Hilda Bourne Engineering Scholarship: merit scholarship for one outstanding woman in engineering}
   \resumeItem{Gallogly College of Engineering Diversity and Inclusion Scholar}
   \resumeItem{OU Women in Engineering Impact in Engineering Award: peer-voted award for outstanding technical project}
   \resumeItem{OU Women in Engineering Outstanding Sophomore: peer-voted award}
   \resumeItem{Mary Enod Williams Classics and Letters Scholarship: merit scholarship for one outstanding classics student}
   \resumeItem{CAMWS Award for Outstanding Accomplishment in Classical Studies}
   \resumeItem{Phi Beta Kappa: national arts and sciences honor society}
   \resumeItem{Tau Beta Pi: national engineering honor society}
   \resumeItem{Eta Sigma Phi: national classics honor society}
   \resumeItem{Phi Kappa Phi: national academic honor society}
\resumeItemListEnd
 \resumeSubHeadingListEnd
\end{document}
